% Author : Pranav Suri
% Based off of: https://github.com/sb2nov/resume
% License : MIT

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\evensidemargin}{-0.65in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}  % Adjusted spacing
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\  % Removed \textbf since we'll handle it in the content
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{linkblue}{RGB}{51,102,187}


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Pranav Suri} \\ \vspace{3pt}
    \small 
    \faPhone\ 437-970-9137 $|$ 
    \faEnvelope\ \href{mailto:pranav.suri@uwaterloo.ca}{\color{linkblue}\underline{pranav.suri@uwaterloo.ca}} $|$ 
    \faLinkedin\ \href{https://linkedin.com/in/pranav-suri}{\color{linkblue}\underline{linkedin.com/in/pranav-suri}} $|$
    \faGithub\ \href{https://github.com/pranavsuri4303}{\color{linkblue}\underline{github.com/pranavsuri4303}}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Swift, Objective-C, Kotlin, Dart, Golang, JavaScript, Rust, C++, GraphQL} \\
     \textbf{Technologies/Frameworks}{: SwiftUI, Flutter, Firebase, REST APIs, Gin, gqlgen, Federation, Cocoapods/SPM} \\
     \textbf{Cloud \& DevOps}{: GCP, GitHub Actions, CI/CD, Git, Cloud Functions, MongoDB Atlas} \\
     \textbf{Developer Tools}{: Xcode, Android Studio, Charles Proxy, JIRA, TeamCity, Figma}
    }}
\end{itemize}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  
  \resumeSubheading
    {\textbf{Ecobee} $|$ \emph{Swift, Obhjective-C, GraphQL}}{Apr. 2024 -- Present}
    {Software Engineer}{Remote}
    \resumeItemListStart
      \resumeItem{Migrated legacy asynchronous code from PromiseKit to Swift’s async/await pattern, streamlining data flow and resolving concurrency bugs across 15+ SwiftUI screens.}
      \resumeItem{Integrated Generac suite functionality into the Eco+ platform with features like grid outage protection and amplitude event handling. Identified and resolved edge-case bugs to ensure seamless operation across connected devices.}
      \resumeItem{Diagnosed and resolved 10+ high-priority bugs, including UI rendering issues, API failures, and incorrect data mappings, improving system stability and user experience.}
      \resumeItem{Refactored shared UI components and improved internal design system tooling, reducing code duplication by 30\%, preventing regressions, and accelerating feature delivery.}
    \resumeItemListEnd

    \resumeSubheading
    {\textbf{CourtIQ} $|$ \emph{Swift, Golang, Javascript, GraphQL, MongoDB $|$ \href{https://github.com/CourtIQ/courtiq-ios}{\color{linkblue}\faGithub}
    }}{2023 -- Present}
    {Founder and Engineer}{Remote}
    \resumeItemListStart
    \resumeItem{Designed a scalable backend architecture with Golang, Apollo Federation, and MongoDB, managing 5+ microservices.}
    \resumeItem{Automated CI/CD pipelines with Docker, Makefile, and GCP, deploying seamlessly to Google Cloud Run.}
      \resumeItem{Developed a modular design system in SwiftUI and integrated Apollo Client for GraphQL code generation, ensuring consistent UI/UX and efficient backend communication in iOS apps.}      
      \resumeItem{Integrated Firebase Auth and FCM for secure user authentication and real-time notifications, while enabling advanced search with MongoDB Atlas Search for faster data retrieval.}
      \resumeItem{Managed end-to-end development as the sole contributor, owning backend services, iOS app development, and Figma-based design systems for a cohesive project delivery.}
    \resumeItemListEnd

    \resumeSubheading
      {\textbf{Ecobee} $|$ \emph{Swift, Obhjective-C, GraphQL}}{Aug. 2023 -- Present}
      {Software Engineer}{Remote}
      \resumeItemListStart
      \resumeItem{Developed ActivityKit live activity prototype with GraphQL subscriptions for real-time home monitoring alerts.}
      \resumeItem{Eliminated 20+ redundant feature flags and established documentation protocol to improve codebase efficiency.}
      \resumeItem{Developed 11 SwiftUI screens for a smart doorbell product and 5+ shared UI components for the design system.}
    \resumeItemListEnd
      
    \resumeSubheading
      {\textbf{1Password} $|$ \emph{Swift, Objective-C, Rust, Azure}}{Sep. 2022 -- Jan. 2023}
      {Software Developer Intern}{Remote}
      \resumeItemListStart
      \resumeItem{Developed key user lifecycle features in Swift, Objective-C, and Rust, improving user onboarding and retention metrics.}
      \resumeItem{Built cross-platform QR code authentication system in Swift and Rust during company hackathon.}
      \resumeItem{Collaborated with product and design teams to scope features and plan sprints for a 20-person engineering team.}
    \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Capybara (Pre-seed Startup)} $|$ \emph{Swift, Golang, PostgreSQL, AWS}}{Aug. 2022 -- Oct. 2022}
      {Lead iOS Developer}{Singapore}
      \resumeItemListStart
        \resumeItem{Spearheaded development of iOS application, translating $>$20 Figma frames into code using SwiftUI.}
        \resumeItem{Introduced atomic UI design principles and refactored legacy SwiftUI code to enhance application performance and maintainability, leading to more efficient and effective code reuse.}
        \resumeItem{Created an SPM networking library with caching and MVVM, optimizing API data flow and reducing server calls.}
        \resumeItem{Assisted in development and bug fixes for RESTful API developed using Golang and PostgreSQL.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Autotrader.ca} $|$ \emph{Swift, Objective-C, PagerDuty, New Relic, Azure, Cocoapods }}{Jan. 2022 -- May 2022}
      {iOS Engineering Intern}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Fixed iPad search sorting and built remote config caching system to optimize feature flag performance.}
        \resumeItem{Used feature flags to track system appearance preferences, driving the implementation of dark mode support.}
        \resumeItem{Developed autofill features for registration and subscriptions, resulting in 5\% increase in user conversion.}
        \resumeItem{Executed UI tests and biweekly regression testing, while monitoring system health using New Relic and PagerDuty.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Leadership \& Extracurricular}
    \resumeSubHeadingListStart
    \resumeSubheading
    {\textbf{Sigma Chi(Leadership Fraternity)}}{Jan 2023 – Present}
    {President}{University of Waterloo}
    \resumeItemListStart
    \resumeItem{Managed a \$$1,000,000$ property, overseeing the maintenance, servicing, and overall operational efficiency while overseeing key improvement projects.}
    \resumeItem{Administered a termly budget of ~\$$40,000$, allocating resources for essential upgrades and spearheading initiatives like a \$$20,000$ energy-efficient furnace installation to reduce costs and enhance sustainability.}
    \resumeItem{Provided leadership and strategic oversight, fostering collaboration among members and alumni to drive property improvements and long-term sustainability.}
  \resumeItemListEnd

  \resumeSubheading
    {\textbf{BSJ Eco Committee - Weather and Pollution Station Team}}{Fall 2019 – Spring 2021}
    {Project Lead}{British School Jakarta}
  \resumeItemListStart
    \resumeItem{Curated documentation for troubleshooting and maintenance of \$$10,000$ weather and pollution station.}
    \resumeItem{Implemented automation of data collection with the help of Python Selenium \& BeautifulSoup4.}
    \resumeItem{Develop website and mobile app to provide live pollution and weather update along with predictions to community.}
  \resumeItemListEnd

  \resumeSubheading
    {\textbf{BSJ Eco Committee - Weather and Pollution Station Team}}{Fall 2019 – Spring 2021}
    {Project Lead}{British School Jakarta}
  \resumeItemListStart
    \resumeItem{Participate in inter-school, local, national, and international competitions.}
    \resumeItem{Doubles specialist, coach for HS varsity doubles team \& Assistant tournament director for monthly tournaments at HS.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{TMDB movie Appd} $|$ \emph{Swift, Dart, Kotlin $|$ \href{https://github.com/pranavsuri4303/tmdb-declarative-ui}{\color{linkblue}\faGithub}
    }}{January 2021}
    \resumeItemListStart
    \resumeItem{Built a movie app using SwiftUI, Jetpack Compose, and Flutter to compare declarative UI frameworks, displaying "Now Playing" and "Popular" movies via The Movie Database API.}
    \resumeItem{Used MVVM architecture across all platforms to manage state and streamline development while analyzing the strengths and limitations of each framework.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

  %-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {\textbf{University of Waterloo}}{Waterloo, Canada}
    {BSc, Minor in Economics}{Apr. 2026}
  \resumeSubheading
    {\textbf{British School Jakarta}}{Jakarta, Indonesia}
    {IB Diploma \& IGCSE}{Spring 2021}
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
